Prestige bias in cultural evolutionary dynamics

### 2024-05-06 ms/ms.tex
finished revision

\begin{figure}[h]
    \includegraphics[width=0.9\linewidth]{kimura_var.pdf}
  \caption{\textbf{Fixation probability and time in a constant environment.}
	The effect of the success-bias weight $\alpha$ (bottom x-axis) and effective population size, $N_e$, (top x-axis) on the fixation probability (\textbf{A}) and the conditional fixation time (\textbf{B}), and the effect of the success coefficient, or effective selection coefficient, $1-\beta$, on the fixation probability (\textbf{B}) and the conditional fixation time (\textbf{D}).
	Our approximation (black; \cref{eq:kimura_p}) agrees with both DMD simulations (green) and Wright-Fisher simulations (orange).
	Panel A shows a dashed line at $2(1-\beta)$, which is reached by our approximation when $\alpha=1$.
	Panel B has three lines: solid for our approximation for $\alpha=0.01$, and dashed for $\alpha=0$ (bottom) and $\alpha=0.02$ (top).
	Markers are averages of $10,000$ simulations. Error bars show 95\% confidence intervals for panels A and B and 75\% for panels C and D.
   	Here, population size is $N=1,000$; 
	In panels A and B, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$);
	In panels C and D, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}, $\alpha=0.01$.
   }
  \label{fig:var_alpha}
\end{figure}

@@

{\small
\section*{Acknowledgements}
We thank Marc Feldman, Martin Pontz, Gili Greenbaum, Alon Rozen, Tal Simon and two anonymous reviewers for discussions and comments.
This work was supported in part by 
Minerva Stiftung Center for Lab Evolution~(YR) and  the John Templeton Foundation~(YR 61809).
}

>>>>

\begin{figure}[h]
    \includegraphics[width=0.9\linewidth]{kimura_var.pdf}
  \caption{\textbf{Fixation probability and time in a constant environment.}
	The effect of the success-bias weight $\alpha$ (bottom x-axis) and effective population size, $N_e$, (top x-axis) on the fixation probability (\textbf{A}) and the conditional fixation time (\textbf{B}), and the effect of the success coefficient, or effective selection coefficient, $1-\beta$, on the fixation probability (\textbf{B}) and the conditional fixation time (\textbf{D}).
	Our approximation (black; \cref{eq:kimura_p}) agrees with both DMD simulations (green) and Wright-Fisher simulations (orange).
	Panel A shows a dashed line at $2(1-\beta)$, which is reached by our approximation when $\alpha=1$.
	Panel B has three lines: solid for our approximation for $\alpha=0.01$, and dashed for $\alpha=0$ (bottom) and $\alpha=0.02$ (top).
	Markers are averages of $10,000$ simulations. Error bars show 95\% confidence intervals.
	Here, population size is $N=1,000$; 
	In panels A and B, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$);
	In panels C and D, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}, $\alpha=0.01$.
   }
  \label{fig:var_alpha}
\end{figure}

@@

{\small
\section*{Acknowledgements}
We thank Marc Feldman, Martin Pontz, Gili Greenbaum, Alon Rozen, Tal Simon and three anonymous reviewers for discussions and comments.
This work was supported in part by 
Minerva Stiftung Center for Lab Evolution~(YR) and  the John Templeton Foundation~(YR 61809).
}
